Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-04-10 ref_response/ProjectNarrative.tex
Update ref report after telecon

\textbf{[1] Near the end of the introduction and at the beginning of the conclusion we include the phrase, ``The strength of this project is its ability analyze GWs hundreds of milliseconds post bounce from multiple progenitors while accurately accounting for rotation and neutrinos" to more explicitly outline what makes our project unique from previous works.}\\

@@

\textbf{We agree that the GW signal and PNS evolution will be affected.  As a caveat, we add a reference to Muller et al. 2013 that points out that the peak GW frequency from GR effective potential is underestimated, compared to xCFC, while preserving the GW amplitude and PNS compactness (in beginning of Section 3.4).  Nevertheless, the GR effective potential has been shown to accurately reproduce results from the neutron star migration test (Marek et al. 2006, O'Connor \& Couch 2018).}\\

@@

\textbf{[10] We associate this signal with strong prompt convection that occurs within the first 25 ms post bounce.  This signal appears clearly as the bright region in Figure 6 for all rotational velocities.  This fact is noted in Section 3.5.}\\

>>>>

\textbf{[1] Near the end of the introduction and at the beginning of the conclusion we include the phrase, ``The strength of this project is its ability analyze GWs hundreds of milliseconds post bounce from multiple progenitors while accurately accounting for rotation and neutrinos.  The wide breadth of parameter space we examine allows us to reveal certain rotational effects on the GW signal in the context of a controlled study" to more explicitly outline what makes our project unique from previous works.}\\

@@

\textbf{We agree that the GW signal and PNS evolution will be affected.  As a caveat, we add a reference to Muller et al. 2013 that points out that the peak GW frequency from GR effective potential is overestimated, compared to xCFC, while preserving the GW amplitude and PNS compactness (in beginning of Section 3.4).  Nevertheless, the GR effective potential has been shown to accurately reproduce results from the neutron star migration test (Marek et al. 2006, O'Connor \& Couch 2018).}\\

@@

\textbf{[10] This signal appears clearly as the bright region in Figure 6 for all rotational velocities and in Figure 11.  This fact is noted in Section 3.5.}\\
